biological data preperation

### 2018-09-18 src/biological_data_prep.Rmd
fixed the issue with projecting the species data to aea

Load the env. data
```{r}
library(raster)
cell_layer <- raster("../output/env/unique_cell.tif") #this is loading the cell layer that was created and saved as a tif
plot(cell_layer)
```
The occurrence data needs to be converted into s spatialpoints dataframe
```{r}
library(sp)
xy <- adddata[ ,c(2,3)]
spatial_data <- SpatialPointsDataFrame(coords = xy, data = adddata, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))
spatial_data
```
ok now you should probably reproject the data into the same projection as the env. data
```{r}
spatial_data_aea <- spTransform(spatial_data, CRS = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #note -60 used to be -91. Changed to 'straighten up'
```
Ok now plot the env. and point data...
```{r}
plot(cell_layer)
plot(spatial_data_aea$decimalLatitude, spatial_data_aea$decimalLongitude)
plot(spatial_data$decimalLongitude,spatial_data$decimalLatitude)
```
oh it doesn;t work... it should be in meters now?

>>>>

Load the env. data
```{r}
library(raster)
cell_layer <- raster("../output/env/unique_cell.tif") #this is loading the cell layer that was created and saved as a tif
plot(cell_layer)
```
The occurrence data needs to be converted into s spatialpoints dataframe
```{r}
library(sp)
xy <- adddata[ ,c(3,2)] #3 = decimalLongitude, 2 = decimalLatitude
spatial_data <- SpatialPointsDataFrame(coords = xy, data = adddata, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))
spatial_data
```
ok now you should probably reproject the data into the same projection as the env. data
```{r}
spatial_data_aea <- spTransform(spatial_data, CRS = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #note -60 used to be -91. Changed to 'straighten up'
spatial_data_aea
```
```{r}
plot(spatial_data_aea, axes=TRUE, cex.axis=.95)
write.csv(spatial_data_aea, file = "../output/bio/aea_data.csv", row.names = FALSE)

```

Ok now plot the env. and point data...
```{r}
plot(cell_layer)
points(spatial_data_aea$decimalLongitude, spatial_data_aea$decimalLatitude)
```
Write the transformed species data to a new csv (this will also have the coordinates in meters - note meters are under decimalLongitude1 and decimalLatitude1)
```{r}
write.csv(spatial_data_aea, file = "../output/bio/adddata_aea.csv", row.names = FALSE)
```
